\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-08-25 doc/sw-system.tex
added todo note for myself

Adopting the online stage 1 analysis, and the offline stage 2 analysis, we
show in \Fref{fig:results:sample:CP} a plot of completeness versus purity in
the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
varies along the curves. Completeness is defined as the number of correctly
detected sims divided by the total number of sims in the training set, while
purity is the number of correct detections divided by the total number of
detections. \footnote{The completeness is equivalent to the TPR and is also
known elsewhere as the `recall'. The purity is also known as the `precision'.}
If the training set samples from the same systems as the test set, then the
completeness of the training set will be equivalent to the completeness of the
test set. The purity depends on the proportion of sims to duds, and so the
purity of the test set must be approximated by rescaling the training set to
the expected proportion of lens systems to not-lens systems in the survey. 
First we compute the expected number of false positives by multiplying the FPR
by the expected number of non-lenses in the survey. Then we multiply the TPR
by the expected number of lenses in the survey, to get the expected number of
true positives. The sum of the true positives and the false positives gives
the expected sample size; dividing the expected number of true positives by
this sample size gives the purity. Note that the completeness is invariant to
this transformation.

>>>>

Adopting the online stage 1 analysis, and the offline stage 2 analysis, we show
in \Fref{fig:results:sample:CP} a plot of completeness versus purity in the two
stages. As in \Fref{fig:results:sample:roc}, the detection threshold varies
along the curves. Completeness is defined as the number of correctly detected
sims divided by the total number of sims in the training set, while purity is
the number of correct detections divided by the total number of
detections.\footnote{The completeness is equivalent to the TPR and is also
known elsewhere as the `recall'. The purity is also known as the `precision'.}
If the training set samples from the same systems as the test set, then the
completeness of the training set will be equivalent to the completeness of the
test set. The purity depends on the proportion of sims to duds, and so the
purity of the test set must be approximated by rescaling the training set to
the expected proportion of lens systems to not-lens systems in the survey.
First we compute the expected number of false positives by multiplying the FPR
by the expected number of non-lenses in the survey. Then we multiply the TPR by
the expected number of lenses in the survey, to get the expected number of true
positives. The sum of the true positives and the false positives gives the
expected sample size; dividing the expected number of true positives by this
sample size gives the purity. Note that the completeness is invariant to this
transformation.

\todo{Chris}{Write analysis of completeness purity.}
